---
title: "R Notebook"
output: html_notebook
---

# LIBRARIES

```{r}
library(tidyverse)
library(RMySQL)
library(odbc)
library(DBI)
```

# IMPORTING THE DATASET

```{r}
library("openxlsx")
library("readxl")
coronavirus_tweets <- read_excel("full_dataset.xlsx")
str(coronavirus_tweets)
```

# CREATING THE AWS CONNECTION

WE ARE CONNECTING TO AWS.

```{r}
connection <- DBI::dbConnect(
    RMySQL::MySQL(), 
    host = "database-ncrivera-stu.c1oquv6wmh3w.us-east-1.rds.amazonaws.com", 
    dbname = "NRiveraDatabase",
    port = 3306, 
    user = "admin", 
    password = "n1088191"
)
```


# CHECKING THE TABLES WITHIN THE DATABASE


```{r}
tables <- dbListTables(connection)
sort(tables)
```

# CREATING A TABLE TO HOUSE THE DATASET GENERATED

```{r}
dbCreateTable(connection, name = "coronavirus", fields = coronavirus_tweets, row.names = NULL)
```


# CHECKING THE TABLE TO CONFIRM EXISTENCE

```{r}
corona <- dbReadTable(connection,  "coronavirus")
head(corona)
str(corona)
```


```{r}
# dbWriteTable(
#     conn = connection, 
#     name = "coronavirus", 
#     value = coronavirus_tweets, 
#     append = TRUE, 
#     row.names = FALSE
# )
```



```{r}
# library("openxlsx")
# library("readxl")
# query <- dbSendQuery(conn = connection, statement = "SELECT * FROM coronavirus;")
# coronavirus_tweets <- dbFetch(query, n = -1)

coronavirus_tweets <- read_excel("full_dataset.xlsx")
# dbClearResult(query)
```

# Text Analysis

```{r}
library(tidyverse)
library(stringr)
library(tm)
library(quanteda)
```

# CHecking the Dataset

```{r}
str(coronavirus_tweets)
```

# COUNT SPACES and OCCURRENCES

```{r}
negative_words <- 
    
    sum(str_detect(coronavirus_tweets$text, "kung|kung flu|wuhan|wuhan flu|chinavirus|evil"))

cat("Number of tweets with 'Chinavirus':", cnt_chinavirus, "\n")
```


# HOW MANY HASHTAGS?

```{r}
sum(str_detect(coronavirus_tweets$text, '#'))
```

# NUMBER OF MENTIONS

```{r}
sum(str_detect(coronavirus_tweets$text, '@'))
```

# CORPUS CREATION

```{r}
tweetCorpus <- Corpus(VectorSource(coronavirus_tweets$text))
tweetTDM <- TermDocumentMatrix(tweetCorpus)
inspect(tweetTDM)
```

 

# DOCUMENT FEATURE MATRIX

```{r}
tweetDFM <- dfm(coronavirus_tweets$text,
                remove_punct = TRUE,
                remove = stopwords("english"))
```

 

# TOP FEATURES

```{r}
topfeatures(tweetDFM)
```

 

#  WEIGHT FREQUENCY 

Now we have structured data to work with  

```{r}
textstat_frequency(tweetDFM)
```

 


# SELECTING #China

```{r}
sum(str_detect(
  coronavirus_tweets$text, 'lie')
)

 

ChinaTweets <- 
  subset(coronavirus_tweets,
         str_detect(
           text,
           regex('lie',
                 ignore_case = TRUE)
         ))

 


head(select(ChinaTweets, text))
```

```{r}
sum(str_detect(coronavirus_tweets$text, "death|lie|china|spread|pandemic|outbreak|cause|disease|harm|killed|fake|tough"))
```

```{r}
coronavirus_twts <- coronavirus_tweets %>% 
    mutate(negative_tweet = if_else(str_detect(text, "death|lie|china|spread|pandemic|outbreak|cause|disease|harm|killed|fake|tough") == TRUE, true = 1, false = 0)) %>% 
    mutate(keyword_count = str_count(text, "death|lie|china|spread|pandemic|outbreak|cause|disease|harm|killed|fake|tough")) %>% filter(negative_tweet == 1) %>% 
    group_by(created) %>% 
    summarize(count = n())
    
```

```{r}
coronavirus_twts %>% View()
```

```{r}
# install.packages("lda")
# install.packages("reshape2")
# install.packages("syuzhet")
library(ggplot2)
library(tidyverse)
library(lda)
library(reshape2)
require("ggplot2")
require("reshape2")
require("lda")
library("SnowballC")
library("tm")
library("twitteR")
library("syuzhet")
library(caTools)
library(rpart)
library(rpart.plot)
library(e1071)
```


# READING IN THE IMPORTED DATA

```{r}
read <- read.xlsx("full_dataset.xlsx")
head(read)
```

# Delete all the URLs, hashtags and other twitter handles

```{r}
tweets.df2 <- gsub("http.*","",read$text)
tweets.df2 <- gsub("https.*","",tweets.df2)
tweets.df2 <- gsub("#.*","",tweets.df2)
tweets.df2 <- gsub("@.*","",tweets.df2)
```

# Get the emotion scores for  each tweets, breaks the emotion into 10 different emotions – anger, anticipation, disgust, fear, joy, sadness, surprise, trust, negative and positive.

```{r}
word.df <- as.vector(tweets.df2)
emotion.df <- get_nrc_sentiment(word.df)
emotion.df2 <- cbind(tweets.df2, emotion.df) 
```


# Extract sentiment score for each of the tweets, and category into three types, Negative, Positive and Neutral

```{r}
sent.value <- get_sentiment(word.df)

category_senti <- ifelse(sent.value < 0, "Negative", ifelse(sent.value > 0, "Positive", "Neutral"))
```

# Combine the origianl file, sentiment scores and sentiment category

```{r}
category_senti2 <- cbind(read,category_senti,sent.value)
head(category_senti2)
table(category_senti2$category_senti)
```

# DEFINING THE NEW VARIABLES

Define new variable Negative, when sentiment socre <0, equal to TRUE, when sentiment score >0, equal to FALSE
Define new variable Positive, when sentiment socre >0, equal to TRUE, when sentiment score <0, equal to FALSE

```{r}
category_senti2$Negative <- as.factor(category_senti2$sent.value < 0)
category_senti2$Positive <- as.factor(category_senti2$sent.value > 0)
category_senti2
```

# Create a Corpus, convert the text to lowercase, remove all punctuation and stem the words.

```{r}
corpus <- Corpus(VectorSource(category_senti2$text))
corpus <- tm_map(corpus, tolower)
corpus <- tm_map(corpus, removePunctuation)
stopwords("english")[1:10]
corpus <- tm_map(corpus, stemDocument)
corpus[[1]]
```

# Build a document term matrix, called DTM

```{r}
DTM <- DocumentTermMatrix(corpus)
DTM
inspect(DTM)
```
# Remove sparse terms, and convert the DTM to a data frame

```{r}
inspect(DTM[1000:1005, 505:515])
sparse_DTM <- removeSparseTerms(DTM, 0.995)
sparse_DTM
tweetsSparse <- as.data.frame(as.matrix(sparse_DTM))
tweetsSparse
```

# Add the dependent variable, which is Negative, and Positive

```{r}
colnames(tweetsSparse) <- make.names(colnames(tweetsSparse))
tweetsSparse$Negative <- category_senti2$Negative
tweetsSparse$Positive <- category_senti2$Positive
table(tweetsSparse$Negative)
table(tweetsSparse$Positive)
```

# Split data in training/testing sets, for Negative and Positive tweets

```{r}
set.seed(123)

splitNegative <- sample.split(tweetsSparse$Negative, SplitRatio = 0.7)
trainSparseNegative <- subset(tweetsSparse, splitNegative == TRUE)
testSparseNegative <- subset(tweetsSparse, splitNegative == FALSE)

splitPositive <- sample.split(tweetsSparse$Positive, SplitRatio = 0.7)
trainSparsePositive <- subset(tweetsSparse, splitPositive == TRUE)
testSparsePositive <- subset(tweetsSparse, splitPositive == FALSE)
```


# The CTREE Molde for Negative and Positive

```{r}
# For Nagetive tweets
tweetCARTNegative <- rpart(Negative ~ . , data = trainSparseNegative, method = "class")
prp(tweetCARTNegative)

# Prediction
predictCARTNegative <- predict(tweetCARTNegative, newdata = testSparseNegative, type = "class")

cmat_CARTNegative <- table(testSparseNegative$Negative, predictCARTNegative)
cmat_CARTNegative 
```

```{r}
# For Positive
tweetCARTPositive <- rpart(Positive ~ . , data = trainSparsePositive, method = "class")
prp(tweetCARTPositive)

# Prediction
predictCARTPositive <- predict(tweetCARTPositive, newdata = testSparsePositive, type = "class")

cmat_CARTPositive <- table(testSparsePositive$Positive, predictCARTPositive)
cmat_CARTPositive
```


# Logistic Regression Model and Prediction for Negative and Positive

```{r}
# For Nagetive tweets
tweetLogN <- glm(Negative ~ . , data = trainSparseNegative, family = "binomial")
summary(tweetLogN)
# Prediction
tweetLog_predict_testN <- predict(tweetLogN, type = "response", newdata = testSparseNegative)

cmat_logRegrN <- table(testSparseNegative$Negative, tweetLog_predict_testN > 0.5)
cmat_logRegrN

```

```{r}
# For Positive 
tweetLogP <- glm(Positive ~ . , data = trainSparsePositive, family = "binomial")
summary(tweetLogP)

# Prediction
tweetLog_predict_testP <- predict(tweetLogP, type = "response", newdata = testSparsePositive)

cmat_logRegrP <- table(testSparsePositive$Positive, tweetLog_predict_testP > 0.5)
cmat_logRegrP
```



# Naive Bayes 

```{r}
# For Nagetive tweets
tweetNBN <- naiveBayes(Negative~., data = trainSparseNegative)
tweetNBN
```

# Prediction

```{r}
# perform on the testing set
nb_prediction <- predict(tweetNBN, testSparseNegative, type="class")

#confusion matrix
table(testSparseNegative$Negative, nb_prediction, dnn=c("Actual", "Prediction"))

#output results
data.frame(testSparseNegative, Prediction = nb_prediction)

```


```{r}
# For Positive tweets
tweetNBP <- naiveBayes(Positive~., data = trainSparsePositive)
tweetNBP

# Prediction
cmat_NBP <- table(testSparsePositive$Positive, tweetNBP > 0.5)
cmat_NBP
```

# Interaction Effect: Non-Linear Regression

```{r}
colnames(trainSparsePositive)
inter_model <- lm(medv ~ lstat * rm * ptratio + I(lstat ^ 2) + I(rm ^ 2) + I(ptratio ^ 2), data = Boston)
summary(inter_model)

linear_model <- lm(Positive ~ . , data = trainSparsePositive)
step(object = linear_model, direction = "backward")
```

# K-Means Clustering

```{r}
coronavirus_cluster_data <- data.frame(favorited = coronavirus_tweets$favoriteCount, retweetNumber = coronavirus_tweets$retweetCount)
corona_clusters <- kmeans(coronavirus_cluster_data, centers = 2, nstart = 25)
corona_clusters
```

# Interaction with Logistic Regression

```{r}
# Randomly Selecting Variables
sample(colnames(trainSparsePositive$Positive), size = 3) # [1] "estabelecimento", "kill", "even"

interaction_model <- glm(Positive ~ estabelecimento * kill * even + I(estabelecimento ^ 2) + I(kill ^ 2) + I(even ^ 2), 
                         data = trainSparsePositive, family = "binomial")
summary(interaction_model)
```

```{r}
interaction_model_negative <- glm(Negative ~ estabelecimento * kill * even + I(estabelecimento ^ 2) + I(kill ^ 2) + 
                                      I(even ^ 2),data = trainSparseNegative, family = "binomial")
summary(interaction_model)
```

